Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-04-24 manuscript/manuscript.tex
Modified determination of D and delta in manuscript

In order to determine default values for the distance-size ratio ($D$)
and the delta ratio ($\delta$) that ensure both numerical accuracy and 
computation effectiveness we need to compare the numerical 
approximation with some analytical solutions.

On the homogeneous density tesseroids case, \citet{Uieda2016} and 
\citet{Grombein2013} compared their numerical models with the analytical 
solution of a spherical shell.
We could follow this idea, but for our needs the spherical shell must 
have the same density function as the numerical model.
In contrast with the homogeneous density case, the analytical solutions 
for a variable density spherical shell must be obtained.

We will then perform these comparisons between the analytical solutions 
and the numerical model for specific density functions: a linear and an 
exponential one.
And from these results we will finally obtain default values for $D$ 
and $\delta$ that ensure a numerical error lower than 0.1\%.

>>>>

The discretization algorithms described on the previous section are 
introduced to improve the accuracy of the numerical approximation of 
the gravitational fields.
They involve two predefined ratios that determine how many 
times each tesseroid will be discretized and thus indirectly control 
the numerical error of the approximation.
The modified version of the adaptive discretization algorithm involves  
the distance-size ratio $D$, while the density-based discretization 
algorithm makes use of the delta ratio $\delta$.
These algorithms need default predefined values for $D$ and $\delta$ 
in order to ensure both acceptable numerical accuracy and computation 
effectiveness.

On the homogeneous density tesseroids case, \citet{Uieda2016} compared 
their numerical model with the analytical solution of a spherical 
shell in order to obtain default values for the distance-size ratio 
$D$.
We could follow this idea, but for our needs the spherical shell must 
have the same density function as the numerical model.
In contrast with the homogeneous density case, the analytical solutions 
for a variable density spherical shell must be obtained.

We will then perform these comparisons between the analytical solutions 
and the numerical model for specific density functions: a linear and an 
exponential one.
From these results we will finally obtain default values for $D$ 
and $\delta$ that ensure a numerical error lower than 0.1\%.
